Current document extraction benchmarks focus on short, key-value forms, leaving long-list entity extraction, the recovery of hundreds or sometimes thousands of repeated records from tables and mixed layouts, underexplored. Business documents such as loss runs, invoices, and itemized bills commonly contain such lists. We introduce LongListBench, a synthetic benchmark for long-list extraction that pairs structured ground truth (JSON) with rendered documents and paired clean and OCR transcripts. This supports evaluation under complex layouts and OCR noise, while making OCR-specific degradation measurable without changing the underlying document.
The benchmark injects seven document phenomena observed in production (page breaks, multi-row entities, duplicates, large documents, distractor tables, multi-column layouts, and merged cells) to stress segmentation and schema-conformant extraction at scale. Using corpus-level field-value micro-averaging as the primary metric, a local full-context one-shot Gemini baseline on the OCR condition reaches 27.4\% $F_1$ overall and 5.9\% on the extreme tier, while a local auto-chunked Gemini baseline reaches 84.8\% overall and 81.7\% on the extreme tier. Chunking therefore substantially improves robustness on very long documents, but the simpler released baseline still leaves major residual errors, especially on long detailed documents, and should be viewed as a mitigation rather than a complete solution. We further evaluate a third, agentic regime in which GPT-5.5 is given only the OCR inside a code-execution sandbox and parses the document with its own tools rather than via fixed chunking; it reaches 90.6\% overall and 89.4\% on the extreme tier, the strongest result we observe, though as a more capable model it measures regime and model jointly.
%
