For each PDF, the system must reconstruct the complete target list under a declared output contract. Predictions use \texttt{incidents} for claim tasks and \texttt{records} for operations, external loss-run, and policy tasks.

\subsection{Input condition}
Every PDF has a released OCR transcript. Experiments may instead use direct PDF input or another OCR system, but must report the input condition, model, protocol, and included samples.

\subsection{Extraction protocols}
\label{subsec:extraction-protocols}
The repository includes a raw full-context API adapter, an OpenAI Agents SDK sandbox adapter, and repository-denied Codex and Claude Code CLI runners. Four full-corpus CLI results use the same OCR-conditioned protocol.

\paragraph{Full-context one-shot extraction.}
The entire transcript is sent in one request. This is a useful lower-bound calibration, but long outputs may truncate or time out.

\paragraph{Agentic sandbox extraction.}
The runner creates a temporary workspace containing the transcript, field contract, prompt, and output directory. A macOS sandbox profile denies the benchmark repository, while the task prompt prohibits using files outside the workspace. This is repository isolation, not a host-wide filesystem allowlist. The model may search, parse, and verify the current document before writing JSON.

\paragraph{Parser diagnostics.}
Template parsers are useful for structured scale-test families. A frozen parser evaluated on unseen templates measures transfer robustness, while a per-document agent may write code for the current input. These protocols answer different questions and must be labeled separately.

Claim runs receive the published JSON Schema. Generic-record runs receive sample-specific field names and record groups derived from the ground-truth object structure before workspace creation. This exposes the required output schema, not target values or counts. Ground-truth files, generator code, target values, and target counts are not copied into the workspace, and the repository path is denied.

\paragraph{Why use an agentic baseline.}
The largest targets contain thousands of rows, so a single response can hit output or latency limits before returning a complete list. Fixed chunking avoids that limit but introduces chunk size, overlap, boundary repair, and merge parameters that can dominate the result. A per-document sandbox instead lets the extractor choose how to inspect, segment, parse, and verify each new document under one output contract. We use this as a reproducible full-corpus reference protocol, not as a raw measure of either base model alone.

\subsection{Configuration-aware reporting}
Field-pair micro-$F_1$ can hide incomplete records because it gives partial credit and large scale-test families dominate field counts. Reports should lead with exact-record recall and document completion. Secondary reporting includes field diagnostics, predicted counts, configuration and family results, and stressor slices such as \path{cross_section_join}, \path{long_range_evidence}, and \path{heterogeneous_record_list}. We classify four parser-friendly families as scale tests and the remaining seven families as structural challenges using a fixed family mapping.

\subsection{Validation and report regeneration}
Reports are stored as JSON and Markdown. The checker recomputes every metric from saved predictions and ground truth without rerunning a model.

\subsection{Strict completeness and field diagnostics}
The primary metrics are exact-record recall and complete-document success. A predicted record is exact only when every normalized target field equals one ground-truth record. We compute
\begin{align}
\mathrm{ExactRecordRecall} &= \frac{|R_G \cap R_P|}{|R_G|},\\
\mathrm{CompleteDocument} &= \mathds{1}[R_G = R_P],
\end{align}
where $R_G$ and $R_P$ are the normalized ground-truth and predicted record multisets. The intersection preserves duplicate multiplicity, and $\mathds{1}[R_G=R_P]$ is one only when neither records nor duplicates are missing or extra. Source order is not part of the released contract.

For claim incidents, records are keyed by normalized incident identifiers. String values are whitespace-normalized and compared case-insensitively, dates are normalized to \texttt{MM/DD/YYYY}, claimant lists are sorted, zero-valued default financial-breakdown cells are omitted from field diagnostics, and non-zero monetary fields are rounded to cents. Generic records use the same string normalization. Unambiguous domain labels are canonicalized: jurisdiction names to codes, fuel descriptions to parenthetical codes, line-of-business names to acronyms, and visible \texttt{Applies within} wrappers to their core clause scope. Generic records are matched greedily by overlapping non-global field pairs; \texttt{record\_type}, global policy fields, and hidden row identifiers are excluded from field matching and field-pair scoring. These field-level exclusions do not relax exact-record comparison, which uses the full normalized public record.

For secondary partial-credit diagnostics we compute
\begin{align}
\mathrm{found} &= |G \cap P|,\\
\mathrm{recall} &= \frac{\mathrm{found}}{|G|},\\
\mathrm{precision} &= \frac{\mathrm{found}}{|P|},\\
\mathrm{F1} &= \frac{2\,\mathrm{precision}\,\mathrm{recall}}{\mathrm{precision}+\mathrm{recall}},
\end{align}
where $G$ and $P$ are the normalized ground-truth and predicted field-value multisets. Reports also include exact-record precision/$F_1$, predicted counts, missing and extra records, document-macro field $F_1$, and family, evaluation-role, and stressor summaries. Because stressors co-occur, stressor slices describe associations rather than causal effects.
