This revision reports corpus validation and two current OCR-conditioned agentic extraction baselines. Reports from earlier revisions correspond to earlier dataset layouts and should be treated as archival unless rerun on the current 36-document OCR corpus.

Earlier prerelease experiments on an 80-document development version of LongListBench compared full-context one-shot prompting, fixed transcript chunking, and an OpenAI Agents SDK sandbox loop. Those runs helped shape the benchmark by showing that extraction protocol can dominate long-list recall, especially when one-shot prompting is forced to emit hundreds or thousands of rows. We do not mix those numbers into the current results because the released corpus, schemas, document templates, and scoring logic changed substantially. Current method comparisons should be rerun on the released OCR corpus and reported with the input condition, protocol, and manifest hash.

\subsection{Artifact completeness}
The released data directory contains one PDF, one HTML source, one JSON ground-truth file, one per-sample metadata file, and one OCR transcript for each of the 36 manifest instances. The manifest totals are internally consistent: 31{,}961 non-policy target records, 1{,}489 policy target records, and 33{,}450 target records overall.

\begin{table}[H]
\centering
\small
\caption{Current release validation summary.}
\label{tab:release-validation}
\begin{tabular}{@{}lr@{}}
\toprule
Check & Value \\
\midrule
Manifest instances & 36 \\
PDF artifacts & 36 \\
HTML artifacts & 36 \\
Ground-truth JSON files & 36 \\
OCR transcripts & 36 \\
Total target records & 33{,}450 \\
Released transcript condition & OCR \\
Average identifier coverage & 100.0\% \\
Tracked identifier-field support & 99.9\% \\
Records with missing tracked OCR identifiers & 39 \\
Unrecoverable numeric GT values in OCR & 0 \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Benchmark coverage}
The largest family, IFTA mileage by vehicle, contributes 17{,}565 target records across 8 PDFs. The remaining core operations families add return schedules, tax summaries, multisection IFTA return packets, driver/MVR rosters, vehicle schedules, and external loss-run rows. These documents stress high-density extraction where the main failure mode is list completeness across many pages.

Some operations families are intentionally structured reports. Deterministic row parsers can perform well on parts of these files, especially when OCR preserves table headers and row boundaries. We therefore treat them as scale and completeness cases rather than as the primary evidence for hard semantic extraction. The harder regimes are the claim and policy packets, where target records require inherited context, heterogeneous schemas, distant supporting sections, and distractor material.

The multi-hop cases stress a different failure mode. The claim packets contain only 77 target incidents, but the evidence for each incident is distributed across distant packet sections. The policy packets contain 1{,}489 multi-hop policy records across BOP, WC, and CGL packets. These policy documents make the target schema heterogeneous: a system must recover locations, coverage items, forms, material clauses, endorsements, class-code rows, exposure items, and premium records rather than one repeated row shape.

OCR validation checks whether tracked identifiers from the ground truth are visible in the released transcripts. All 36 samples pass the 95\% identifier-coverage threshold, with 100.0\% average identifier coverage and 99.9\% support across tracked identifier field instances. The affected-record count is more conservative: 39 of 33{,}450 records have at least one tracked identifier missing from OCR, mostly because a small number of repeated section headers or row identifiers were not transcribed. We also run a numeric-fidelity gate over all ground-truth numeric values with absolute value at least 10; the current release has 0 unrecoverable numeric values under that check. These validations bound the released OCR transcript condition before extraction scoring; they are not extraction scores. Extraction runs are evaluated first by complete normalized records, then by flattened field-value pairs for partial credit.

\subsection{Current OCR extraction baselines}
\label{subsec:current-ocr-baseline}
We ran the same per-document protocol with two coding agents on all 36 released documents. Each received one OCR transcript and the public field contract in a temporary workspace, while a macOS sandbox denied the benchmark repository. Ground truth, target values and counts, and generator code were not copied into the workspace. Each agent could inspect the transcript, write temporary code, validate JSON, and return the complete record list. The saved \texttt{codex\_gpt55} run used Codex CLI with \texttt{gpt-5.5} and xhigh reasoning, completed July 1, 2026. The \texttt{claude\_opus48} run used Claude Code CLI with \texttt{claude-opus-4-8} and xhigh effort, completed July 12, 2026. Claude Code safe mode disabled custom instructions, skills, plugins, hooks, and MCP servers. These are protocol baselines, not raw one-shot model measurements.

\begin{table}[H]
\centering
\footnotesize
\caption{Full-corpus agentic OCR baselines. Strict completeness is primary; field micro-$F_1$ is secondary partial credit.}
\label{tab:agentic-full-corpus}
\begin{tabular}{@{}p{0.37\linewidth}rrrrr@{}}
\toprule
Protocol & Docs & Records & Exact records & Complete docs & Field F1 \\
\midrule
Codex CLI \texttt{gpt-5.5}, xhigh reasoning & 36 & 33{,}450 & 89.5\% & 12/36 (33.3\%) & 98.7\% \\
Claude Code \texttt{opus-4-8}, xhigh effort & 36 & 33{,}450 & 86.9\% & 13/36 (36.1\%) & 98.6\% \\
\bottomrule
\end{tabular}
\end{table}

The strict result changes the interpretation of the apparently high field scores. Codex and Claude recover 89.5\% and 86.9\% of records with every normalized target field correct, yet only about one-third of documents are complete. The field-pair metric remains near 99\% because it gives partial credit to records with one or more wrong fields.

We partition document families by their intended design rather than a numerical score threshold. Scale controls contain repeated structured rows and test volume, OCR preservation, and output completeness. Structural challenges require enrichment, reconciliation, inherited context, heterogeneous records, or cross-section joins.

\begin{table}[H]
\centering
\scriptsize
\caption{Strict completeness by evaluation role. Exact records are corpus-level exact-record recall within each role.}
\label{tab:agentic-by-role}
\begin{tabular}{@{}p{0.22\linewidth}rrrrrr@{}}
\toprule
Role & Docs & Records & Codex exact & Claude exact & Codex complete & Claude complete \\
\midrule
Structural challenges & 21 & 10{,}745 & 68.9\% & 60.7\% & 2/21 (9.5\%) & 3/21 (14.3\%) \\
Scale controls & 15 & 22{,}705 & 99.3\% & 99.3\% & 10/15 (66.7\%) & 10/15 (66.7\%) \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}[H]
\centering
\scriptsize
\caption{Agentic OCR results by document family. Exact-record recall is primary; field-pair $F_1$ shows partial correctness. The rule separates structural challenges (above the divider) from scale controls (below it).}
\label{tab:agentic-by-regime}
\begin{tabular}{@{}p{0.31\linewidth}rrrrrr@{}}
\toprule
Document family & Docs & Records & Codex exact & Claude exact & Codex F1 & Claude F1 \\
\midrule
Driver/MVR request and roster & 3 & 1{,}260 & 1.9\% & 0.0\% & 89.1\% & 88.3\% \\
Claim cross-page multi-hop & 3 & 77 & 32.5\% & 98.7\% & 97.1\% & 99.9\% \\
IFTA return schedule details & 5 & 4{,}923 & 65.2\% & 63.9\% & 97.7\% & 97.1\% \\
External loss run & 3 & 900 & 71.4\% & 93.9\% & 97.2\% & 99.7\% \\
IFTA tax return inquiry detail & 2 & 1{,}300 & 97.7\% & 90.8\% & 99.4\% & 95.5\% \\
Policy multi-hop & 3 & 1{,}489 & 96.4\% & 32.0\% & 99.8\% & 99.4\% \\
IFTA multisection return packet & 2 & 796 & 99.9\% & 99.9\% & 100.0\% & 100.0\% \\
\midrule
IFTA tax return summary & 4 & 3{,}040 & 96.0\% & 99.9\% & 99.7\% & 100.0\% \\
Driver schedule spreadsheet export & 1 & 500 & 99.4\% & 99.4\% & 99.9\% & 99.9\% \\
IFTA mileage by vehicle & 8 & 17{,}565 & 99.8\% & 99.1\% & 100.0\% & 99.7\% \\
Vehicle schedule spreadsheet export & 2 & 1{,}600 & 100.0\% & 100.0\% & 100.0\% & 100.0\% \\
\bottomrule
\end{tabular}
\end{table}

The strict metric exposes failures hidden by partial credit. Driver/MVR packets have 1.9\% and 0.0\% exact-record recall because roster rows require sparse MVR enrichment; return schedules reach only 65.2\% and 63.9\% because surcharge fields and some rows are omitted. In contrast, the multisection cross-section join reaches 99.9\% for both agents after canonicalizing equivalent jurisdiction and fuel labels, so that construction does not challenge these systems. The packet families reverse by agent: Codex scores 96.4\% on policies but 32.5\% on claims, while Claude scores 32.0\% and 98.7\%. A family label therefore does not define a universal difficulty ordering.

Cross-cutting slices show the same system dependence. Cross-section joins and repeated keys score 99.9\% for both agents. Heterogeneous lists score 96.4\% for Codex and 32.0\% for Claude; long-range evidence scores 93.3\% and 35.2\%; split records score 85.9\% and 78.6\%; inherited context scores 85.6\% and 78.7\%. These are associations, not causal effects, because tags overlap and some slices contain only a few documents. A controlled estimate would require paired renderings of the same records with and without one stressor.

Full-context one-shot extraction is not a practical full-corpus protocol for this release. The small claim packet and one driver/MVR packet returned scoreable outputs, but larger claim packets reached the model output limit and loss-run samples timed out under the same one-shot setup. This is expected for a benchmark containing documents with hundreds to thousands of target records: the one-shot condition is a lower-bound operational stress test, not the primary protocol for full-document evaluation. Future method papers should compare per-document agentic, retrieval-loop, and verification-based systems under the same OCR input condition.
