LongListBench is a measurement tool for long-list extraction under controlled synthetic conditions. Table~\ref{tab:benchmark-scope} summarizes the current scope.

\begin{table}[H]
\centering
\caption{Scope of the current LongListBench release.}
\label{tab:benchmark-scope}
\begin{tabular}{>{\raggedright\arraybackslash}p{0.46\linewidth} >{\raggedright\arraybackslash}p{0.46\linewidth}}
\toprule
Covered & Not covered / out of scope \\
\midrule
High-density repeated lists, cross-section joins, long-range evidence packets, and mixed-schema output lists & Non-English documents, handwriting, medical bills, invoices, purchase orders, and many other document families \\
Production-like synthetic layouts based on observed document structures & Full visual diversity of private production corpora and carrier-specific edge cases \\
OCR transcripts for every released PDF, including a limited scanned-image IFTA condition & Multiple OCR engines, broad scan-quality sweeps, bounding boxes, and reading-order supervision \\
Strict normalized-record completeness plus field diagnostics & Source-order scoring, semantic equivalence, downstream task metrics, and human adjudication of ambiguous fields \\
Agentic sandbox support and four full-corpus OCR baselines & Latency/cost-normalized comparisons across broader agentic and retrieval-loop protocols \\
\bottomrule
\end{tabular}
\end{table}

The documents are synthetic. This is necessary for public release, but it means the benchmark cannot replace evaluation on a private production corpus. We used private documents only as structural references for layout and packet organization; the released names, identifiers, values, and prose are generated. Some sections are intentionally composed to cover benchmark stressors, so the corpus should be read as production-inspired measurement data rather than exact replicas of source documents.

The current release includes one OCR transcript condition. This supports reproducible OCR-conditioned evaluation, but it does not isolate OCR penalty by itself. Measuring OCR penalty requires adding another transcript or direct-PDF condition and running the same extraction protocol across both.

The released output contract treats records as an unordered multiset. Exact-record and complete-document metrics therefore test values and multiplicity, not source order. An order-sensitive task should declare ordering in the contract and rerun extractors under that requirement rather than retroactively penalizing the saved predictions.

The coding-agent runs denied access to the benchmark repository but did not use a host-wide filesystem allowlist. Ground truth remained inside the denied repository. Future comparisons should use an allowlisted container or virtual machine and retain tool traces; the Claude result format did not include them.

OCR support should also be interpreted at the field level. A unique-identifier coverage check can look strong while a missing section header affects many records that inherit that header. The current validation reports unique identifier coverage, affected records for tracked identifiers, and a numeric-fidelity gate over ground-truth numeric values with absolute value at least 10. Richer future releases should extend this with row-local OCR checks and multiple OCR engines.

Finally, the corpus now contains several operations record types whose public schema is represented by the ground-truth examples and generic scorer rather than separate hand-written JSON Schema files for every family. Adding explicit schemas for each operations family would improve reproducibility for prompt-based and agentic extractors.

LongListBench is intended for configuration-, family-, and stressor-aware measurement of record completeness, field alignment, OCR-conditioned extraction, and long-range evidence handling. Parser-friendly operations families are scale tests; claims about difficult extraction should rely on packet and cross-section families as well as aggregate scores.

Complexity slices are observational. Tags overlap, and document families differ in length, schema, and layout, so lower performance in a tagged slice does not identify one stressor as the cause. Paired renderings that hold records constant while adding one stressor would be required for causal attribution.

The release is not a complete model leaderboard. It includes GPT-5.5, GPT-5.6-Sol, Opus 4.8, and Fable 5 under one agentic protocol, but no latency- or cost-normalized comparison across broader models and protocols. Full-context one-shot runs are impractical on the largest outputs, and synthetic public documents cannot replace private production evaluation.
